%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This is a modified ONE COLUMN version of
% the following template:
%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
      \documentclass[]{deedy-resume-openfont}
  
      \begin{document}
      
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  %
  %     Profile
  %
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  
\namesection{Sai} {Rahul Nallandhighal}\infoline{\href{mailto:mkssps42@gmail.com}{mkssps42@gmail.com} | 8499036028 | 3-125/87/1/57/1, Streetno:5, Lecturers Colony,Boduppal}\\\vspace{4pt}\linksline{\descript{\href{https://github.com/KOAwesome}{GitHub | }}\descript{\href{https://www.linkedin.com/in/sai-rahul-nallandhighal/}{Linkedin | }}\descript{\href{https://leetcode.com/mkssps42/}{LeetCode | }}\descript{\href{https://www.hackerrank.com/mkssps42}{HackerRank}}}\underlineheader{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Education
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education}
\raggedright

    \runsubsection{Malla Reddy Engineering College}\hspace*{\fill}  \location{Nov 2020 - Present}\\
    \descript{Computer Science loT, B.Tech}\hspace*{\fill}\location{Hyderabad, India}\\
    CGPA: 8.5\\
    \sectionsep
  

    \runsubsection{Sri Chaitanya Junior College}\hspace*{\fill}  \location{2018 - 2020}\\
    \descript{MPC, Intermediate Education}\hspace*{\fill}\location{Hyderabad, India}\\
    Percentage: 93\%\\
    \sectionsep
  

    \runsubsection{Sri Sai Public School}\hspace*{\fill}  \location{2008 - 2018}\\
    \descript{ICSE High School}\hspace*{\fill}\location{Hyderabad, India}\\
    Percentage: 88\%\\
    \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Skills
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Skills}
\raggedright
\begin{longtable}{p{5cm}p{13.5cm}}
\descript{Programming Languages} & {\location{Java, Python, Shell Scripting, C++}} \\
\descript{Libraries/Frameworks} & {\location{Java Script, Django, Numpy, Pandas, Seaborn, Matplotlib}} \\
\descript{Tools / Platforms} & {\location{Nmap, Nessus, Burpsuite, Wireshark.}} \\
\descript{Databases} & {\location{MySql}} \\
\end{longtable}
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
        %
        %     Projects
        %
        %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
        \section{Projects / Open-Source}
        \raggedright
        
            \runsubsection{\large{Smart Saline Monitoring System}}
            \descript{| \href{https://github.com/KOAwesome/Smart-Saline-Monitoring-System}{Link}}\hfill \location{Arduino, HX711, LCD, I2C, GSM}\\
            \begin{tightemize}
\item  In emergency times, hospitals will be flooded with patients and sometimes the hostel may be understated, our team designed a smart automation which informs the responsible person about the details of saline bottle.
\item  Developed a weight monitoring system using Arduino and HX711 load cell sensor to measure weight accurately. Integrated an LCD display for real-time weight visualization and a GSM module to send SMS notifications when weight thresholds are exceeded.
\end{tightemize}
            \sectionsep
          
        
            \runsubsection{\large{A Novel Web Attack Detection System}}
            \descript{| \href{https://github.com/KOAwesome/A-Novel-Web-Attack-Detection-System}{Link}}\hfill \location{Python, Django}\\
            \begin{tightemize}
\item  We are living in a world where things are connected together with the help of Internet, smart watches, smart TVs are today\textquotesingle{}s normal.
\item  So with convenience, there is also a risk, the communication between various devices is easily susceptible to various attacks. I developed a model in Python which identifies the different types of attacks.
\item  I used data sheets from keggle website
\end{tightemize}
            \sectionsep
          
        
            \runsubsection{\large{Quiz Generator}}
            \descript{| \href{https://github.com/KOAwesome/Quiz-Generator}{Link}}\hfill \location{Python-docx, python3}\\
            \begin{tightemize}
\item  During covid times, education is pertained to home. Students were given excel sheets which contain objective question bank.
\item  Reading from the excel sheet provides no interaction and is ineffective. I designed a program which can generate quiz from the excel sheet provided to it. It is console based. It removes the questions from excel if we answer them right.
\end{tightemize}
            \sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Certifications
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Certifications}
\vspace{4pt}
\begin{tightemize}
\item NPTEL Online Certification Python for Data Science - \descript{\href{https://drive.google.com/file/d/18eUHqC2QtSAs2ADX401i\_NORVOAxcpkN/view?usp=share\_link}{IIT Madras}}\\
\item NPTEL Online Certification Ethical Hacking - \descript{\href{https://drive.google.com/file/d/18c0hokOsa4\_ATjbI7dFbXX0rOkJf4xv8/view?usp=share\_link}{IIT Kharagpur}}\\
\item Introduction to Programming using python - Microsoft Certifications.\\
\item Azure Fundamentals - Microsoft Certifications.\\
\end{tightemize}
\vspace{4pt}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Awards
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Honors \& Awards}
\vspace{4pt}
\begin{tightemize}
\item Won inter college Basket ball for 2 consecutive years.\\
\item Achieved a 5 star rating on Hacker Rank platform in Java programming language\\
\end{tightemize}
      \ 
      \end{document}