\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \usepackage[hidelinks]{hyperref}
    \usepackage[left=2cm, right=2cm, top=2cm]{geometry}
    \usepackage{longtable}
    \textheight=10in
    \pagestyle{empty}
    \raggedright

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}

% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
    \vspace*{-40pt}

    

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Profile
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \vspace*{-2pt}
  \begin{center}
    {\Huge \scshape {Sai Rahul Nallandhighal}}\\
    \vspace*{2pt}
    
    \vspace*{2pt}
    \href{mailto:mkssps42@gmail.com}{mkssps42@gmail.com} | \href{tel:8499036028}{8499036028} | 3-125/87/1/57/1, Streetno:5, Lecturers Colony,Boduppal\\
    \vspace*{2pt}
    \textbf{\href{https://www.linkedin.com/in/sai-rahul-nallandhighal/}{Linkedin | }}\textbf{\href{https://leetcode.com/mkssps42/}{LeetCode | }}\textbf{\href{https://www.hackerrank.com/mkssps42}{HackerRank | }}\textbf{\href{https://github.com/KOAwesome}{GitHub}}\\
  \end{center}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %
    %     Education
    %
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
      \header{Education}
      \vspace{2mm}
      \textbf{Malla Reddy Engineering College}\hfill Hyderabad, India\\
Computer Science loT, B.Tech \hfill Nov 2020 - Present\\
{\sl CGPA: 8.5}\\
\vspace{2mm}
      \textbf{Sri Chaitanya Junior College}\hfill Hyderabad, India\\
MPC, Intermediate Education \hfill 2018 - 2020\\
{\sl Percentage: 93}\%\\
\vspace{2mm}
      \textbf{Sri Sai Public School}\hfill Hyderabad, India\\
ICSE High School \hfill 2008 - 2018\\
{\sl Percentage: 88}\%\\
\vspace{2mm}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Skills
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \header{Skills}
  \vspace{2mm}
  \begin{longtable}{p{4cm}p{12cm}}
  Programming Languages: & Java, Python, Shell Scripting, C++ \\
  Libraries/Frameworks: & Java Script, Django, Numpy, Pandas, Seaborn, Matplotlib \\
  Tools / Platforms: & Nmap, Nessus, Burpsuite, Wireshark. \\
  Databases: & MySql \\
  \end{longtable}
  \vspace{1mm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %
    %     Projects
    %
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
      \header{Projects / Open-Source}
      \vspace{2mm}
      {\textbf{Smart Saline Monitoring System}}\textbf{ | \href{https://github.com/KOAwesome/Smart-Saline-Monitoring-System}{Link}}\hfill{\sl Arduino, HX711, LCD, I2C, GSM}\\
          \vspace{-3mm}
\begin{itemize} \itemsep -3pt
\item  In emergency times, hospitals will be flooded with patients and sometimes the hostel may be understated, our team designed a smart automation which informs the responsible person about the details of saline bottle.
\item  Developed a weight monitoring system using Arduino and HX711 load cell sensor to measure weight accurately. Integrated an LCD display for real-time weight visualization and a GSM module to send SMS notifications when weight thresholds are exceeded.
\end{itemize}
          \vspace*{3mm}
      {\textbf{A Novel Web Attack Detection System}}\textbf{ | \href{https://github.com/KOAwesome/A-Novel-Web-Attack-Detection-System}{Link}}\hfill{\sl Python, Django}\\
          \vspace{-3mm}
\begin{itemize} \itemsep -3pt
\item  We are living in a world where things are connected together with the help of Internet, smart watches, smart TVs are today\textquotesingle{}s normal.
\item  So with convenience, there is also a risk, the communication between various devices is easily susceptible to various attacks. I developed a model in Python which identifies the different types of attacks.
\item  I used data sheets from keggle website
\end{itemize}
          \vspace*{3mm}
      {\textbf{Quiz Generator}}\textbf{ | \href{https://github.com/KOAwesome/Quiz-Generator}{Link}}\hfill{\sl Python-docx, python3}\\
          \vspace{-3mm}
\begin{itemize} \itemsep -3pt
\item  During covid times, education is pertained to home. Students were given excel sheets which contain objective question bank.
\item  Reading from the excel sheet provides no interaction and is ineffective. I designed a program which can generate quiz from the excel sheet provided to it. It is console based. It removes the questions from excel if we answer them right.
\end{itemize}
          \vspace*{3mm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
      %
      %     Certifications
      %
      %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
      \header{Certifications}
      \vspace{2mm}
      • NPTEL Online Certification Python for Data Science - \textbf{\href{https://drive.google.com/file/d/18eUHqC2QtSAs2ADX401i\_NORVOAxcpkN/view?usp=share\_link}{IIT Madras}}\\
\vspace*{1mm}
      • NPTEL Online Certification Ethical Hacking - \textbf{\href{https://drive.google.com/file/d/18c0hokOsa4\_ATjbI7dFbXX0rOkJf4xv8/view?usp=share\_link}{IIT Kharagpur}}\\
\vspace*{1mm}
      • Introduction to Programming using python - Microsoft Certifications.\\
\vspace*{1mm}
      • Azure Fundamentals - Microsoft Certifications.\\
\vspace*{1mm}
      \vspace{2mm}

\header{Honors \& Awards}
      \vspace{2mm} 
      Won inter college Basket ball for 2 consecutive years.\\
\vspace*{1mm}
      Achieved a 5 star rating on Hacker Rank platform in Java programming language\\
\vspace*{1mm}

    \ 
    \end{document}